Rank verification for exponential families

### 2016-04-19 verifying-winner.tex

\begin{abstract}
This paper deals with the selective inference problem encountered in rank verification --- verifying the order of the natural parameters in exponential families. We constructed a selective level-$\alpha$ test for verifying the largest natural parameter, which provides familywise error rate (FWER) and false discovery rate (FDR) control as we extend it into a step-down procedure. We also provide selective confidence bound for the difference between the largest and the second largest natural parameters.
\end{abstract}

@@

We often make observations that form a joint distribution. While it might be relatively obvious in the independent case, the observations can well be dependent, complicating comparisons of parameters. However, comparison of these parameters can produce useful inferences.

A classic question is on how to statistically verify empirical rankings based on simple exponential family models. As motivation, consider a 2016 Quinnipiac University poll of $890$ Iowa Republicans Poll. \cite{quinnipiac} The poll found that Trump was in the lead with $31\%$ of the vote, Cruz is the first runner-up with $24\%$, followed by Rubio at $17\%$. The other ten candidates, including ``Don't know'', trailed behind. \Cref{tbl:poll} shows the results of the poll. Note that we have made a simplifying assumption that poll represents a random sample of Iowa Republicans --- i.e.\ that the data are multinomial, with parameter $\left(\pi_{\text{Trump}}, \pi_{\text{Cruz}}, \pi_{\text{Rubio}}, \ldots\right)$ representing their support in the Iowa Republican population. In reality, Quinnipiac University Poll Institute has processed the data to make the sample more representative of the population of likely voters.

@@

Having observed that Trump received the most votes in this poll, we want to ask whether he indeed enjoys the most support among all Iowa Republicans. Intuitively, we would compare Trump to Cruz, as well as the other candidate. This intuitive method however has a couple of issues.

\item This has a hidden upward selection bias, or ``winner's curse'', as we are only testing this hypothesis as Trump is leading in the polls. In other words, the hypothesis itself is random. Alternatively, we can note that the marginal type I error rate is not quite straightforward. Specifically, the null hypothesis is ``$H_0 \left(X\right): \text{Leader in polls has most support}$'', which is dependent on random poll data $X$ through $j^*\left(X\right)$, the leader in polls. Then for any distribution $F$ the marginal type I error rate is

\begin{equation}
\PP_F\left(\text{reject } H_0\right) = \sum_{\substack{j \text{ is a candidate} \\ j \text{ does not have most support}}} \PP_F\left(\text{reject } H_0 \middle| j \text{ leads in polls}\right) \PP_F \left(j \text{ leads in polls}\right).
\label{eqn:marginal_error}
\end{equation}

\item Comparing Trump to all other candidates involves multiple comparisons. Without considering the structure of this problem, common methods that perform multiple comparisons may largely decrease the test power.

We will construct a test as outlined by Fithian, Sun and Taylor in \cite{Fithian:2014ws}. The fundamental idea is to consider the selective type I error rate
$$\PP_F\left(\text{reject } H_0 \middle| j \text{ leads in polls} \right), ~~~~~~~~ \text{where $j$ is a candidate,}$$
instead. Note that controlling this selective type I error rate at $\alpha$ provides control of the marginal type I error rate at $\alpha$ too. From \Cref{eqn:marginal_error},
\begin{align}
\PP_F\left(\text{reject } H_0\right) & = \sum_{\substack{j \text{ is a candidate} \\ j \text{ does not have most support}}} \PP_F\left(\text{reject } H_0 \middle| j \text{ leads in polls}\right) \PP_F \left(j \text{ leads in polls}\right). \nonumber \\
& \le \sum_{\substack{j \text{ is a candidate} \\ j \text{ does not have most support}}} \alpha \PP_F \left(j \text{ leads in polls}\right). \nonumber \\
& = \alpha \PP\left(\text{Leader in polls does not have most support}\right) \nonumber \\
& \le \frac{n-1}{n} \alpha. \label{eqn:selective_vs_marginal}
\end{align}

Surprisingly, this also tackles the second issue above. The test reduces the multiple comparison problem into one comparison between Trump and Cruz. In fact, if 100 John Does entered the race with practically no support from the Iowa Republicans, the change in number of candidates will not change the test.

More generally, when we observe a random vector $(X_1, \ldots, X_n)$ from an exponential family, and whichever random variable is largest, we want to test whether it is in fact stochastically larger than the other random variables.

@@

\subsection{Main result}

In this paper, we focus on Schur-concave exponential family, a broad class of distribution that is defined in \Cref{sec:exponential_families} and includes various examples listed in \Cref{sec:applications}. We constructed a selective level-$\alpha$ test for verifying that the largest observation is stochastically largest as well. The test provides selective type I error control, as well as enables us to construct confidence bound on the differences between the natural parameters and verify the order of the rest of the natural parameters. \WFcomment{Still feels a bit abstract when you discuss these goals here.} \KHcomment{What if we don't mention the side results at all?}

@@

Next we condition on the sufficient statistics for the nuisance parameter, in other words, we consider the conditional law
$$\mathcal{L}_{\pi_1 = \pi_j}\left(\frac{X_1 - X_j}{2} \middle| X_2, \ldots, \frac{X_1 + X_j}{2}, \ldots, X_n, A_1\right),$$
or equivalently, the conditional law
$$\mathcal{L}_{\pi_1 = \pi_j}\left(X_1 \middle| X_2, \ldots, \frac{X_1 + X_j}{2}, \ldots, X_n, A_1\right),$$
which is the distribution $\text{Binomial}\left(X_1 + X_j, \frac{1}{2}\right)$ truncated by the event $A_1$. The one-sided $p$-value $p_{1j}$ is thus given as
\begin{align*}
p_{ij}\left(x_1, \ldots, x_n\right) & = \PP\left(X_1 \ge x_1 \middle| X_2 = x_2, \ldots, \frac{X_1 + X_j}{2} = \frac{x_1 + x_j}{2}, \ldots, X_n = x_n, A_1\right) \\
& = \frac{\sum_{t = x_1}^{x_1 + x_j} \binom{x_1 + x_j}{t} \left(\frac{1}{2}\right)^{x_1 + x_j}}{\sum_{t = \left(x_1 + x_j\right)/2}^{x_1 + x_j} \binom{x_1 + x_j}{t} \left(\frac{1}{2}\right)^{x_1 + x_j}} \\
& = \frac{\sum_{t = x_1}^{x_1 + x_j} \binom{x_1 + x_j}{t}}{\sum_{t = \left(x_1 + x_j\right)/2}^{x_1 + x_j} \binom{x_1 + x_j}{t}},
\end{align*}
and to account for the tie-breaking we adopted earlier, we
\begin{itemize}
\item multiply the first term in the numerator and the denominator by $1/k$ where $k$ is the number of observations tied for largest; otherwise,
\item multiply the first term in the denominator by $1/2$ if $X_1$ and $X_j$ has the same parity, as the sum starts $X_1 = X_j = \frac{x_1 + x_j}{2}$.
\end{itemize}
Noticing that if $X_1, \ldots, X_j$ all tied the $p$-value is $1$, and the denominator is really $1/2$ otherwise \WFcomment{I don't think that's true for $j \neq 2$, is it?} \KHcomment{The denominator should always be half of a binomial distribution I think}, we can write
$$p_{1j} = 1 \wedge 2 \sum_{t=X_1}^{X_1 + X_j} \binom{X_i + X_j}{t}.$$

@@

\Cref{fig:power} gives the power curves for $\text{Multinomial}\left(m, \pi\right)$ and
$$\pi \propto \left(e^\delta, 1, \ldots, 1\right),$$
for various combinations of $m$ and $n$. For Gupta and Nagel, we use $\alpha = 0.05$; but in light of the extra factor of $\frac{n-1}{n}$ in \Cref{eqn:selective_vs_marginal}, we will apply the selective procedure with $\frac{n}{n-1} \alpha$ such that the marginal type I error rate of both procedures are controlled at $\alpha$. \WFcomment{Can we justify this? Our procedure has error $\alpha$ in the case where all $\pi_j$ are equal.} \KHcomment{The selective error rate is $\alpha$, but Gupta and Nagel really only had marginal error rate. If all $\pi_j$ are equal, the marginal error rate is $\frac{n-1}{n} \alpha$.} Gupta and Nagel coincides with our test at $n = 2$; however as $n$ grows, the selective test shoes significantly more power than Gupta and Nagel's test.

@@

We would like to extend the result from multinomials to exponential families. We henceforth focus on exponential distribution taking the form
\begin{equation}
X \sim \exp\left(\theta_1 X_1 + \cdots + \theta_n X_n\right) g\left(X\right) h\left(\theta\right),
\label{eqn:exp_family}
\end{equation}
defined on the Lebesgue or counting measure. It is reasonable to assume that the family is ``symmetric'', i.e.\ if $\theta_j = \theta_k$, then the probability distribution remains the same when $X_j$ and $X_k$ are swapped. This corresponds to requiring $g\left(X\right)$ to be symmetric. We would also like to introduce a fairly mild additional condition that $g$ is {\em Schur-concave}. But first we recall the notion of {\em majorization}, defined on both $\mathbb{R}^n$ and $\mathbb{Z}^n$. \WFcomment{I think we're implicitly assuming here  that $g$ is a density wrt one of (a) Lebesgue or (b) counting measure. Is that right? And if so, do we need a couple sentences to explain why it works in the counting measure case? That is, we need the atoms of non-zero measure to match up with each other along the rays of interest, right?} \KHcomment{We are making those assumptions. For Lebesgue, there should be no atoms. For counting measure, they should all line up perfectly. I don't think this result generalizes very well for other measures.}

>>>>

\begin{abstract}
Many statistical experiments involve comparing of multiple population groups. For example, a public opinion poll may ask which of several political candidates commands the most support in a given population, or a clinical trial may compare patient outcomes under several treatment conditions. This article concerns the problem of {\em rank verification} --- post hoc tests of whether the ordering discovered in the data is in fact statistically significant. For exponential family models, we show under mild conditions that an unadjusted two-tailed pairwise $p$-value comparing the ``winning'' population to the ``runner-up'' is a valid $p$-value for checking whether the winner is truly the best. We extend this result to provide lower confidence bounds on the gap between the ``winning'' population and the others, and propose a simple step-down algorithm for verifying ranks beyond the first.
\end{abstract}

@@

\subsection{Motivating Example: Iowa Republican Caucus Poll}\label{sec:iowa}

On February 1, 2016, Quinnipiac University released a poll of 890 Iowa Republicans regarding their preferred candidate for the Republican presidential nomination \citep{quinnipiac}. The results, shown in Table~\ref{tbl:poll}, placed Donald Trump in the lead with $31\%$ of the vote, with Ted Cruz in second with $24\%$, Marco Rubio in third with $17\%$, and ten other candidates including ``Don't know'' trailing behind. We assume for simplicity that the poll represents a simple random sample of Iowa Republicans, i.e., that the data are a multinomial sample of size $890$ and underlying probabilities $(\pi_{\text{Trump}}, \pi_{\text{Cruz}}, \pi_{\text{Rubio}}, \ldots)$.\footnote{The reality is a bit more complicated: before releasing the data, Quinnipiac has processed it to make the reported result more representative of likely caucus-goers.}

@@

Seeing that Trump leads this poll, several salient questions may occur to us: Is Trump really winning, and if so by how much? And analogously, is Cruz really in second, is Rubio really in third, and so on?

Note that there is implicitly a problem of multiple comparisons here, because if Cruz had led the poll instead, we would be asking a different set of questions. Indeed, the selection issue appears especially pernicious due to the so-called ``winner's curse:'' given that Trump leads the poll, it more likely than not overestimates his support.

Nevertheless, if we blithely ignore the selection issue, we might carry out the following analyses to answer the questions we posed before at significance level $\alpha=0.05$:
\begin{enumerate}
\item {\em Is Trump really winning?} If Trump and Cruz were in fact tied, then Trump's share of their combined 490 votes would be distributed as $\text{Binom}(490, 0.5)$. Because the (two-tailed) $p$-value for this pairwise test is $p=0.006$, we reject the null and conclude that Trump is really winning.
\item {\em By how much?} Using an exact $95\%$ interval for the same binomial model, we conclude Trump has at least $7.5\%$ more support than Cruz (i.e., $\pi_{\text{Trump}} \geq 1.075 \,\pi_{\text{Cruz}}$) and also leads the other candidates by at least as much.
\item {\em Is Cruz in second, Rubio in third, etc.?} We can next compare Cruz to Rubio just as we compared Trump to Cruz (again rejecting because 214 is significantly more than half of 365), then Rubio to Carson, and so on, as a stepdown procedure. The first four comparisons are all significant at level $0.05$, but Paul and Bush are tied so we stop.
\end{enumerate}

Surprisingly, the three procedures described above are all entirely valid despite the implicit multiple-comparisons issue. The remainder of this article is dedicated to justifying them for the multinomial family and many other settings.

\subsection{Generic Problem Setting and Main Result}

Generically, we will consider data drawn from an exponential family model with density
\begin{equation}\label{eq:expfam}
X \sim e^{\theta'x - \psi(\theta)}g(x),
\end{equation}
with respect to either the Lebesgue or counting measure on $\RR^n$. We assume further that $g(x)$ is symmetric. In addition to the multinomial family, \eqref{eq:expfam} also encompasses settings such as comparing independent binomial treatment outcomes in a clinical trial, competing sports teams under a Bradley-Terry model, entries of a Dirichlet distribution, and many more. \WFcomment{Also students taking a test in a Rasch model, after conditioning on how many get each question right. Or comparing the variances of different normal populations.} We will generically use the term {\em population} to refer to the treatment group, sports team, political candidate, etc. represented by a given random variable $X_j$.

As we will see, $\theta_j > \theta_k$ if and only if $X_j$ is stochastically larger than $X_k$, so there is a well-defined stochastic ordering of the populations. We will refer to the population with maximal $\theta_j$ as the {\em best}, and the one with maximal $X_j$ as the {\em winner}. Following the convention in the ranking and selection literature, we assume that if there are multiple largest $\theta_j$, then one is arbitrarily marked as the best. Note that in cases where it is more interesting to ask which is the smallest population --- for example, if $X_j$ is the number of patients on treatment $j$ who suffer a heart attack during a trial --- we can change variables to $-X_j$.

Write the order statistics of $X$ as
\[
X_{[1]} \geq X_{[2]} \geq \cdots \geq X_{[n]},
\]
and define $\theta_{[j]}$ as the entry of $\theta$ corresponding to the $j$th order statistic of $X$ (note $\theta_{[1]}$ might {\em not} equal $\max_j \theta_j$, for example). We assume any ties between entries of $X$ are broken randomly.

In each of the above examples, there is an exact two-tailed pairwise test we would typically apply if testing $\theta_j=\theta_k$ for any two fixed indices. For example, for the multinomial, we would apply the conditional binomial test based on the combined total $X_j+X_k$ as discussed in the previous section, and for independent binomials we would apply Fisher's exact test. More generally, we can condition on the other $n-2$ indices (notated $X_{\setminus \{j,k\}}$) and $X_j+X_k$, and reject the null if $X_j$ is outside the $\alpha/2$ and $1-\alpha/2$ quantiles of the known conditional law $\mathcal{L}_{\theta_j=\theta_k}(X_j \mid X_j+X_k, X_{\setminus\{j,k\}})$. We call this test the (two-tailed) {\em unadjusted pairwise test} since it implicitly assumes the two indices $j,k$ are fixed and is therefore not adjusted for selection. Similarly, inverting this test for all values of $\theta_j-\theta_k$ yields an {\em unadjusted pairwise confidence interval}.\footnote{To avoid trivialities in the discrete case, we assume these procedures are appropriately randomized at the rejection thresholds to give exact level-$\alpha$ control.}

Generalizing the procedures described in Section~\ref{sec:iowa} we obtain the following:
\begin{enumerate}
\item {\em Is the winner really the best?} Carry out the unadjusted pairwise test comparing the winner to the runner-up. If the test rejects at level $\alpha$, conclude that the winner is really the best.
\item {\em By how much?} Construct the unadjusted pairwise confidence interval comparing the winner to the runner-up, and report the lower confidence bound obtained for $\theta_{[1]}-\theta_{[2]}$.
\item {\em Is the runner-up really the second best, etc.?} Continue by comparing the runner-up to the second-runner-up, again using the unadjusted pairwise test, and so on down the list comparing adjacent values. Stop the first time the test accepts.
\end{enumerate}

We now state our main theorem: under a mild technical assumption, the three procedures described above are statistically valid, even accounting for the selection.
\begin{theorem}\label{thm:main}
Assume the model~\eqref{eq:expfam} holds and $g(x)$ is a Schur-concave function. The first procedure has level $\alpha$ conditional on the best population not winning (otherwise an error is impossible). The second procedure gives an exact $1-\alpha$ lower confidence bound for $\theta_{[1]} - \max_{j \neq [1]} \theta_{j}$. The third procedure is a conservative stepdown procedure with familywise error rate (FWER) no larger than $\alpha$.
\end{theorem}

We define Schur-concave functions and discuss their properties in Section~\ref{sec:maj}. Because any log-concave and symmetric function is Schur-concave, Theorem~\ref{thm:main} applies to all of the cases discussed above.

Note that there is an implicit adjustment for selection here, since we are using two-tailed unadjusted tests. If we instead based our tests on an independent realization $X^*$, then we could (for example) use the right-tailed version of the unadjusted pairwise test for the first procedure. Having to use a two-tailed procedure is in some sense unsurprising: Even for $n=2$, it is intuitive that we should have to use the two-tailed test instead of the one-tailed. Indeed, the first procedure is exactly equivalent to the two-tailed test of the fixed hypothesis $\theta_1=\theta_2$.

What may be more surprising is that, no matter how large $n$ is, we do not require any additional adjustment beyond what we already require for $n=2$. Informally, this can possibly be explained by noting that for large $n$, $X_{[2]}$ suffers from a positive selection bias --- a ``runner-up's curse,'' so to speak --- which is nearly as severe as the bias of $X_{[1]}$.

% \begin{enumerate}

% \item This has a hidden upward selection bias, or ``winner's curse'', as we are only testing this hypothesis as Trump is leading in the polls. In other words, the hypothesis itself is random. Alternatively, we can note that the marginal type I error rate is not quite straightforward. Specifically, the null hypothesis is ``$H_0 \left(X\right): \text{Leader in polls has most support}$'', which is dependent on random poll data $X$ through $j^*\left(X\right)$, the leader in polls. Then for any distribution $F$ the marginal type I error rate is

% \begin{equation}
% \PP_F\left(\text{reject } H_0\right) = \sum_{\substack{j \text{ is a candidate} \\ j \text{ does not have most support}}} \PP_F\left(\text{reject } H_0 \middle| j \text{ leads in polls}\right) \PP_F \left(j \text{ leads in polls}\right).
% \label{eqn:marginal_error}
% \end{equation}

% \item Comparing Trump to all other candidates involves multiple comparisons. Without considering the structure of this problem, common methods that perform multiple comparisons may largely decrease the test power.
% \end{enumerate}

% We will construct a test as outlined by Fithian, Sun and Taylor in \cite{Fithian:2014ws}. The fundamental idea is to consider the selective type I error rate
% $$\PP_F\left(\text{reject } H_0 \middle| j \text{ leads in polls} \right), ~~~~~~~~ \text{where $j$ is a candidate,}$$
% instead. Note that controlling this selective type I error rate at $\alpha$ provides control of the marginal type I error rate at $\alpha$ too. From \Cref{eqn:marginal_error},
% \begin{align}
% \PP_F\left(\text{reject } H_0\right) & = \sum_{\substack{j \text{ is a candidate} \\ j \text{ does not have most support}}} \PP_F\left(\text{reject } H_0 \middle| j \text{ leads in polls}\right) \PP_F \left(j \text{ leads in polls}\right). \nonumber \\
% & \le \sum_{\substack{j \text{ is a candidate} \\ j \text{ does not have most support}}} \alpha \PP_F \left(j \text{ leads in polls}\right). \nonumber \\
% & = \alpha \PP\left(\text{Leader in polls does not have most support}\right) \nonumber \\
% & \le \frac{n-1}{n} \alpha. \label{eqn:selective_vs_marginal}
% \end{align}

% Surprisingly, this also tackles the second issue above. The test reduces the multiple comparison problem into one comparison between Trump and Cruz. In fact, if 100 John Does entered the race with practically no support from the Iowa Republicans, the change in number of candidates will not change the test.

% More generally, when we observe a random vector $(X_1, \ldots, X_n)$ from an exponential family, and whichever random variable is largest, we want to test whether it is in fact stochastically larger than the other random variables.

@@

% \subsection{Main result}

% In this paper, we focus on Schur-concave exponential family, a broad class of distribution that is defined in \Cref{sec:exponential_families} and includes various examples listed in \Cref{sec:applications}. We constructed a selective level-$\alpha$ test for verifying that the largest observation is stochastically largest as well. The test provides selective type I error control, as well as enables us to construct confidence bound on the differences between the natural parameters and verify the order of the rest of the natural parameters. \WFcomment{Still feels a bit abstract when you discuss these goals here.} \KHcomment{What if we don't mention the side results at all?}

@@

Next we condition on the sufficient statistics for the nuisance parameter, in other words, we consider the conditional law
$$\mathcal{L}_{\pi_1 = \pi_j}\left(\frac{X_1 - X_j}{2} \middle| X_2, \ldots, \frac{X_1 + X_j}{2}, \ldots, X_n, A_1\right),$$
or equivalently, the conditional law
$$\mathcal{L}_{\pi_1 = \pi_j}\left(X_1 \middle| X_2, \ldots, \frac{X_1 + X_j}{2}, \ldots, X_n, A_1\right),$$
which is the distribution $\text{Binomial}\left(X_1 + X_j, \frac{1}{2}\right)$ truncated by the event $A_1$. The one-sided $p$-value $p_{1j}$ is thus given as
\begin{align*}
p_{ij}\left(x_1, \ldots, x_n\right) & = \PP\left(X_1 \ge x_1 \middle| X_2 = x_2, \ldots, \frac{X_1 + X_j}{2} = \frac{x_1 + x_j}{2}, \ldots, X_n = x_n, A_1\right) \\
& = \frac{\sum_{t = x_1}^{x_1 + x_j} \binom{x_1 + x_j}{t} \left(\frac{1}{2}\right)^{x_1 + x_j}}{\sum_{t = \left(x_1 + x_j\right)/2}^{x_1 + x_j} \binom{x_1 + x_j}{t} \left(\frac{1}{2}\right)^{x_1 + x_j}} \\
& = \frac{\sum_{t = x_1}^{x_1 + x_j} \binom{x_1 + x_j}{t}}{\sum_{t = \left(x_1 + x_j\right)/2}^{x_1 + x_j} \binom{x_1 + x_j}{t}},
\end{align*}
and to account for the tie-breaking we adopted earlier, we
\begin{itemize}
\item multiply the first term in the numerator and the denominator by $1/k$ where $k$ is the number of observations tied for largest; otherwise,
\item multiply the first term in the denominator by $1/2$ if $X_1$ and $X_j$ has the same parity, as the sum starts $X_1 = X_j = \frac{x_1 + x_j}{2}$.
\end{itemize}
Noticing that if $X_1, \ldots, X_j$ all tied the $p$-value is $1$, and the denominator is really $1/2$ otherwise \WFcomment{I don't think that's true for $j \neq 2$: say $X=(100, 99, 10)$. Then the denominator is }, we can write
$$p_{1j} = 1 \wedge 2 \sum_{t=X_1}^{X_1 + X_j} \binom{X_i + X_j}{t}.$$

@@

\Cref{fig:power} gives the power curves for $\text{Multinomial}\left(m, \pi\right)$ and
$$\pi \propto \left(e^\delta, 1, \ldots, 1\right),$$
for various combinations of $m$ and $n$. For Gupta and Nagel, we use $\alpha = 0.05$; but in light of the extra factor of $\frac{n-1}{n}$ in \Cref{eqn:selective_vs_marginal}, we will apply the selective procedure with $\frac{n}{n-1} \alpha$ such that the marginal type I error rate of both procedures are controlled at $\alpha$. \WFcomment{Can we justify this? Our procedure has error $\alpha$ in the case where all $\pi_j$ are equal.} \KHcomment{The selective error rate is $\alpha$, but Gupta and Nagel really only had marginal error rate. If all $\pi_j$ are equal, the marginal error rate is $\frac{n-1}{n} \alpha$.}  \WFcomment{Yes OK I think you're right. Because for G \& N the ``marginal error rate'' is defined by arbitrarily marking one of the tied populations as the best and then asking whether that marked one gets into the confidence set.} Gupta and Nagel coincides with our test at $n = 2$; however as $n$ grows, the selective test shoes significantly more power than Gupta and Nagel's test.

@@

We would like to extend the result from multinomials to exponential families. We henceforth focus on exponential distribution taking the form
\begin{equation}
X \sim \exp\left(\theta_1 X_1 + \cdots + \theta_n X_n\right) g\left(X\right) h\left(\theta\right),
\label{eqn:exp_family}
\end{equation}
defined on the Lebesgue or counting measure. It is reasonable to assume that the family is ``symmetric'', i.e.\ if $\theta_j = \theta_k$, then the probability distribution remains the same when $X_j$ and $X_k$ are swapped. This corresponds to requiring $g\left(X\right)$ to be symmetric. We would also like to introduce a fairly mild additional condition that $g$ is {\em Schur-concave}. But first we recall the notion of {\em majorization}, defined on both $\mathbb{R}^n$ and $\mathbb{Z}^n$. \KHcomment{We are making those assumptions. For Lebesgue, there should be no atoms. For counting measure, they should all line up perfectly. I don't think this result generalizes very well for other measures.}
